### 2016-01-20 paper.tex
Add McMasters1980 reference

Mean rotor power coefficients for multiple Reynolds numbers are plotted versus
tip speed ratio in Fig.~\ref{fig:cp-curves}. $C_P$ is shown to increase in
general with $Re$, along with a reduction in the optimal tip speed ratio, due to
the tendency of foils to stall at higher angles of attack at higher $Re$, and
the higher angle of attack ranges seen by the blades at lower $\lambda$. These
effects diminish with increasing $Re$, which is expected as the blade boundary
layers transition to turbulence closer to the leading edge \cite{Lissaman1983,
    Bachant2015-RVAT-Re-dep}, which helps flow remain attached longer as it moves
against the adverse pressure gradient on the suction side of the foil. Note how
at lower tip speed ratios and Reynolds numbers, $C_P$ becomes significantly
negative, which is possible thanks to the speed control of the experimental
setup's servo motor applying negative torque to the rotor.

>>>>

Mean rotor power coefficients for multiple Reynolds numbers are plotted versus
tip speed ratio in Fig.~\ref{fig:cp-curves}. $C_P$ is shown to increase in
general with $Re$, along with a reduction in the optimal tip speed ratio, due to
the tendency of foils to stall at higher angles of attack at higher $Re$, and
the higher angle of attack ranges seen by the blades at lower $\lambda$. These
effects diminish with increasing $Re$, which is expected as the blade boundary
layers transition to turbulence closer to the leading edge \cite{Lissaman1983,
    McMasters1980, Bachant2015-RVAT-Re-dep}, which helps flow remain attached longer
as it moves against the adverse pressure gradient on the suction side of the
foil. Note how at lower tip speed ratios and Reynolds numbers, $C_P$ becomes
significantly negative, which is possible thanks to the speed control of the
experimental setup's servo motor applying negative torque to the rotor.
